\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-22 paper/mswp2012-proposal.tex
added Comparison between existing systems and our project/plattform

This project is accompanied by a scientific study. The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system and how to improve these interactions. The focus hereby is on the usability of an ubiquitous health tracking system that (half-)automatically generates useful data of the habits of the participants. This data should lead to a good basis for future work on the topic. \\
% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

@@

>>>>

This project is accompanied by a scientific study. The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system and how to improve these interactions. The focus hereby is on the usability of an ubiquitous health tracking system that (half-)automatically generates useful data of the habits of the participants. This data should lead to a good basis for future work on the topic. \\
% --------------------------------------------------------------
\pagebreak

\section{Project goals and deliverables}
\label{sect:goals}

@@

\subsection{Approach of this Project}
This project does not follow the same approach as the above mentioned Social Plattforms or Game Consoles.

Both mentioned approaches are combining their plattform or consoles as tool to give people motiviation to do their workout, but do not cover other health aspecets as diet or food at all. \\

The goal of this project is to make people live healthier using motivation hints and a huge fun factor combined with social aspect. All of the mentioned systems are using their methods to sell their products to get a financial benefit out of the project, unlike this project is focusing only on the healthiness of its users, which also means that this project is getting money out of other stakeholders, but not from its users directly. \\

This facts also give the system the ability to focus more on the users needs than other systems and introduce more health-saving-features in the future. The goal should be to sell an attitude to life, but not a product such as remotes, consoles or sport articles. Because of these prerequisites its easier to convince scientific stakeholders like medical universities, hospitals, doctors etc. to participate in such a plattform.
